---
title: "p8105_hw5_qs2261"
author: "Qinting Shen"
date: "2023-11-10"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
library(purrr)
```

### Problem 1
#### Read data
```{r}
homicide_raw = 
  read_csv("./homicide-data.csv") |> 
  janitor::clean_names()
```
the `homicide_raw` has `r nrow(homicide_raw)` observations and `r ncol(homicide_raw)` variables.

```{r}
# total number of homicides 
homicide_raw |> 
  mutate(city_state = paste(city, state, sep = ", ")) |> 
  group_by(city_state) |> 
  summarize(n()) 

# the number of unsolved homicides 
homicide_df = 
  homicide_raw |> 
  mutate(city_state = paste(city, state, sep = ", "),
         disposition = 
           ifelse(disposition %in% c("Closed without arrest", "Open/No arrest"), "unsolved", "solved")
         )|> 
  group_by(city_state, disposition)  |> 
  summarize(obs = n()) |> 
  pivot_wider(
    names_from = disposition, 
    values_from = obs) |> 
  summarize(unsolved)
```


### Peoblem 2
#### Import Data

```{r, message = FALSE}
filename = list.files("data", full.names = TRUE) # create a df containing all file names

importdata = function(path) {
  
  df = read_csv(path) |> 
    janitor::clean_names() |> 
    mutate(file = path)
}

longi_df = map(filename, importdata) |> 
  bind_rows()
```

#### Data Wrangling and Plotting
```{r}
tidy_plot =
  longi_df |> 
  separate(file, into = c("folder","arm","underscore","subject_id","csv"), sep = c(5,8,9,11)) |> 
  mutate(arm_id = paste(arm, subject_id)) |> 
  select(-folder, -underscore, - csv) |> 
  select(arm, subject_id, everything()) |> 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "observation" )|> 
  ggplot(aes(x = week, y = observation, group = arm_id, color = arm))+
    geom_line()

tidy_plot
```

The spaghetti plot shows that the observations on each subject in control group fluctuates but remain stable, while those in experimental group are increasing over time. And compared to control group, the mean values of observations of each subject are higher in experimental group.


### Peoblem 3
#### Create a function
```{r}
set.seed(1)
one_samp = function(n= 30, mu, sigma = 5){
  
  sim_data = tibble(
    x = rnorm(n = n, mean = mu, sd = sigma),
  )
  broom::tidy(t.test(sim_data, mu = 0)) 
}
```

#### mu = 0, repeat 5000 times
```{r warning=FALSE}
ttest_mu_0 =
  rerun(5000, one_samp(mu = 0)) |> 
  bind_rows() |> 
  select(estimate, p.value)
```

#### Repeat for mu = 1,2,3,4,5,6
```{r warning=FALSE}
ttest_result = 
 tibble(true_mean = c(0, 1, 2, 3, 4, 5, 6)
        ) |> 
  mutate(
    output_list = map(.x = true_mean, ~ rerun(5000, one_samp(mu = .x))),
    estimate_df = map(output_list, bind_rows)
    )|>  
  unnest(estimate_df) |> 
  select(-output_list)
```


#### Plot 1: effect size and power 
```{r}
power_plot_df = 
  ttest_result |>
  group_by(true_mean) |>
  summarize(reject = sum(p.value < 0.05)/5000) |>
  ggplot(aes(x = true_mean, y = reject)) +
  geom_point() +
  labs(
    title = "Effect size and power",
    x = "True value of mean",
    y = "Power of test"
  )

power_plot_df
```

The plot shows that the power increases as the true value increases. This is because a larger effect size is associated with increased power, making it easier to detect the statistically significant difference.

#### Plot 2: average estimate of mean and true mean
```{r}
plot_avg_mean= 
  ttest_result |> 
  group_by(true_mean) |> 
  mutate(avg_mean = mean(estimate)) |> 
  ggplot(aes(x = true_mean, y = avg_mean ))+
  geom_point()+
  labs(
    title = "Average estimate of mean and true mean",
    x = "True value of mean",
    y = "Average estimate of mean"
  )

plot_avg_mean
```


#### Plot null rejected
```{r}
plot_null_reject =  
  ttest_result |> 
  filter(p.value < 0.05) |> 
  group_by(true_mean) |> 
  mutate(avg_mean = mean(estimate)) |> 
  ggplot(aes(x = true_mean, y = avg_mean ))+
  geom_point()+
  labs(
    title = "Average estimate of mean and true mean in null rejected samples",
    x = "True value of mean",
    y = "Average estimate of mean"
  )

plot_null_reject
```

The sample average of μ̂ across tests for which the null is rejected is approximately equal to the true value of μ. 

Because these samples are also randomly generated from this normal distribution, and the number of the samples is large, their distribution tend to be symmetric to the true mean. Therefore, their average mean value is still close to the true mean.

